WrapITK: Enhanced languages support\\ for the Insight Toolkit

### 2006-03-24 article/Article.tex
fix some typo
darcs-hash:20060324081819-2fc9d-161f3e6a7a004d287d3b6ab9dcc31a97f0aab329.gz

  \item  The template arguments set is poorly choosen, making sometime impossible
to create a pipeline. In WrapITK, most of the filters have the same input and output
types, and only a few filters allow to change type. This make the types manipulated 
by filters more consistent, and the user should always be able to build his pipeline.

@@

  \item  Names in target laguages are inconsistents. WrapITK use a strict naming
convention which should make easier to identify the template arguments.

@@

  \item  The python's \verb$InsightToolkit$ module is only structured as a big
list of names. It make it nearly unusable in the python interpreter. WrapITK
comes with a new well designed python module easy to use in interpreter, and
aproviding run-time lookup of templated types - thing which can't be easily done
in C++. Additionally, WrapITK ensures that \verb$SmartPointer$s are always
returned and acceptable as input, so no bare pointers are ever exposed to
Python. This is not the case in the standard ITK wrappers.

@@

If WrapITK has been installed, then using it from within python is trivial:
simply issue the command \verb$import itk$, and you are ready to go. This
is because WrapITK installs a pth file in the python \verb$site-packages$ directory so
that python knows where to find the itk scripts.

@@

A more convenient syntaxe for usage in interpreter is also available:
\begin{itemize}
  \item \verb$itk.Image.UC3$
  \item \verb$itk.Image.US3$
\end{itemize}
\verb$itk.Image.UC3$ refere to the same class than \verb$itk.Image[itk.UC, 3]$
but have the advantage to allow to use the tab-completion in the interpreter,
and so let the user easily know which template arguments he can use.
However, this notation is more rigid than the one above and won't let the user
specify the type and the dimension used in a single place, and thus,
should be use only in interpreter.

@@

Losts of classes have a \verb$New()$ method which returns a smart pointer to that class. The
\verb$New()$ method in python has some additional features:
\begin{itemize}
  \item Arguments to the new method are assumed to be filter inputs. So you could
write:
\begin{verbatim}
adder = itk.AddImageFilter[...].New()
adder.SetInput1( readerA.GetOutput() )
adder.SetInput2( readerB.GetOutput() )
\end{verbatim}
or you could write
\begin{verbatim}
adder = itk.AddImageFilter[...].New( readerA.GetOutput(), readerB.GetOutput() )
\end{verbatim}
or even
\begin{verbatim}
adder = itk.AddImageFilter[...].New( readerA, readerB )
\end{verbatim}
In that case, \verb$New$ will use the \verb$GetOutput()$ method of the object, if it
exist, to get the image and set the inputs of the new filter.

@@

and, more important, most of classes can be instanciated and parametered in one line,
which make ITK less verbose, and a lots more easy to use in the interpreter.

@@

To set the same radius for all dimensions, it is possible to use the \verb$*$ python
sequence operator - that way, it is possible to write code independant of dimension.

@@

  \item \verb$itk.strel(d, s)$ is used to create a binary ball structuring of dimension
\verb$d$ and size \verb$s$. Strucutring element support is quite bad currently in WrapITK
and should change in the future. Using \verb$itk.strel$ rather than creating a
\verb$BinaryBallStructuringElement$ directly is recommended to have backward compatibility
when the structuring element type will be changed.

@@

WrapITK define several macros and variable designed to:
\begin{itemize}
  \item make creation of wrappers easy. The syntax is simple enough to get in quickely.
  \item make choice of template arguments explicit. It should be easy to understand
the idea of the author of a wrapper by reading the file.
  \item support mostly transparently the dimensions and types chosen by the user.
\end{itemize}

@@

  \item \verb$WRAP_ITK_ALL_TYPES$ contains all the types selected byt the user.

@@

External projects let the developer access some custom class with the target languages
and is a powerful way to extend WrapITK, test new wrapper, wrap more types, etc.
A nice side effect of wrappers, for contributions\footnote{A nice template for
contributions to the Insight Journal \cite{InsightJournalWebSite} which include the 
temlate code to build wrappers is available at
\url{http://voxel.jouy.inra.fr/darcs/contrib-itk/template/}. Just use the command
{\em darcs get http://voxel.jouy.inra.fr/darcs/contrib-itk/template/ contribName}
and edit the project name in the {\em CMakeLists.txt} file to
begin your new contribution.} for example, is to build {\em all}
the methods of the wrapped classes, and so to be sure everything builds as it should
\footnote{We have found and fixed numbers of bug in ITK while adding
more classes to WrapITK}.

>>>>

  \item  The template arguments set is poorly chosen, making sometime impossible
to create a pipeline. In WrapITK, most of the filters have the same input and output
types, and only a few filters allow to change type. This make the types manipulated 
by filters more consistent, and the user should always be able to build his pipeline.

@@

  \item  Names in target languages are inconsistent. WrapITK use a strict naming
convention which should make easier to identify the template arguments.

@@

  \item  The python's \verb$InsightToolkit$ module is only structured as a big
list of names. It make it nearly unusable in the python interpreter. WrapITK
comes with a new well designed python module easy to use in interpreter, and
providing run-time lookup of templated types - thing which can't be easily done
in C++. Additionally, WrapITK ensures that \verb$SmartPointer$s are always
returned and acceptable as input, so no bare pointers are ever exposed to
Python. This is not the case in the standard ITK wrappers.

@@

If WrapITK has been installed, then using it from within python is trivial:
simply issue the command \verb$import itk$, and you are ready to go. This
is because WrapITK installs a \verb$.pth$ file in the python \verb$site-packages$ directory so
that python knows where to find the itk scripts.

@@

A more convenient syntax for usage in interpreter is also available:
\begin{itemize}
  \item \verb$itk.Image.UC3$
  \item \verb$itk.Image.US3$
\end{itemize}
\verb$itk.Image.UC3$ refere to the same class than \verb$itk.Image[itk.UC, 3]$
but have the advantage to allow to use the tab-completion in the interpreter,
and so let the user easily know which template arguments he can use.
However, this notation is more rigid than the one above and won't let the user
specify the type and the dimension used in a single place, and thus,
should be use only in interpreter.

@@

Lots of classes have a \verb$New()$ method which returns a smart pointer to that class. The
\verb$New()$ method in python has some additional features:
\begin{itemize}
  \item Arguments to the new method are assumed to be filter inputs. So you could
write:
\begin{verbatim}
adder = itk.AddImageFilter[...].New()
adder.SetInput1( readerA.GetOutput() )
adder.SetInput2( readerB.GetOutput() )
\end{verbatim}
or you could write
\begin{verbatim}
adder = itk.AddImageFilter[...].New( readerA.GetOutput(), readerB.GetOutput() )
\end{verbatim}
or even
\begin{verbatim}
adder = itk.AddImageFilter[...].New( readerA, readerB )
\end{verbatim}
In that case, \verb$New$ will use the \verb$GetOutput()$ method of the object, if it
exist, to get the image and set the inputs of the new filter.

@@

and, more important, most of classes can be instantiated and parametered in one line,
which make ITK less verbose, and a lots more easy to use in the interpreter.

@@

To set the same radius for all dimensions, it is possible to use the \verb$*$ python
sequence operator - that way, it is possible to write code independent of dimension.

@@

  \item \verb$itk.strel(d, s)$ is used to create a binary ball structuring of dimension
\verb$d$ and size \verb$s$. Structuring element support is quite bad currently in WrapITK
and should change in the future. Using \verb$itk.strel$ rather than creating a
\verb$BinaryBallStructuringElement$ directly is recommended to have backward compatibility
when the structuring element type will be changed.

@@

WrapITK define several macros and variable designed to:
\begin{itemize}
  \item make creation of wrappers easy. The syntax is simple enough to get in quickly.
  \item make choice of template arguments explicit. It should be easy to understand
the idea of the author of a wrapper by reading the file.
  \item support mostly transparently the dimensions and types chosen by the user.
\end{itemize}

@@

  \item \verb$WRAP_ITK_ALL_TYPES$ contains all the types selected by the user.

@@

External projects let the developer access some custom class with the target languages
and is a powerful way to extend WrapITK, test new wrapper, wrap more types, etc.
A nice side effect of wrappers, for contributions\footnote{A nice template for
contributions to the Insight Journal \cite{InsightJournalWebSite} which include the 
template code to build wrappers is available at
\url{http://voxel.jouy.inra.fr/darcs/contrib-itk/template/}. Just use the command
{\em darcs get http://voxel.jouy.inra.fr/darcs/contrib-itk/template/ contribName}
and edit the project name in the {\em CMakeLists.txt} file to
begin your new contribution.} for example, is to build {\em all}
the methods of the wrapped classes, and so to be sure everything builds as it should
\footnote{We have found and fixed numbers of bug in ITK while adding
more classes to WrapITK}.
